Data-Driven Search-based Software Engineering

### 2018-03-13 doc/tex/msr18/main.tex

\documentclass[sigconf,anonymous,review]{acmart}
\acmConference[ESEC/FSE 2018]{12th Joint Meeting of the European Software Engineering Conference and the ACM SIGSOFT Symposium on the Foundations of Software Engineering}{4--9 November, 2018}{Lake Buena Vista, Florida}

@@

\begin{document}
\title{Data-Driven Search-based Software Engineering}
% \titlenote{Produces the permission block, and
%   copyright information}
% \subtitle{Extended Abstract}
% \subtitlenote{The full version of the author's guide is available as
%   \texttt{acmart.pdf} document}

\author{Vivek Nair, George Mathew, Jianfeng Chen, Markus Wanger, Leando Minku, Tim Menzies}
\affiliation{%
  \institution{North Carolina State University, USA}
  \city{Raleigh} 
  \state{NC} 
  \postcode{27606}
}
\email{}

\begin{abstract}
This paper introduces Data-Driven Search-based Software Engineering (DSE), which combines insights from Mining Software Repositories (MSR) and Search-based Software Engineering (SBSE). While MSR formulates software engineering problems as data mining problems, SBSE reformulates SE problems as optimization problems and use meta-heuristic algorithms to solve them. Both MSR and SBSE share the common goal of providing insights to improve software engineering. The algorithms used in these two areas also have intrinsic relationships.  
We therefore argue that combining these two fields
is useful for situations (a)~which require learning from a large data
source or (b)~when optimizers need to know the lay of the land to find better solutions, faster.

@@

This paper also presents a  resource (tiny.cc/data-se) for exploring DSE.  The resource contains 89 artifacts which are related to DSE,
divided into 13 groups such as requirements engineering, software product lines, software processes.
All the materials in this repository
have been   used in recent software engineering papers; i.e., for all this material, there exist baseline results against which researchers can comparatively assess their new ideas.

%This paper introduces Data-Driven Search-based Software Engineering (DSE) which combines insights from Mining Software Repositories (MSR) and Search-based Software Engineering (SBSE). SBSE reformulates the SE problem as an optimization problem and uses a meta-heuristic algorithm to solve those problems. Both the fields, MSR and SBSE, are concerned with providing insights for software engineers to improve SE tasks. The similar goals of the two fields are one of the major reasons why these two fields should work together. 
%We argue that  combining these two fields is useful for situations (a)~which require learning from a large data source or (b)~when optimizers need to know the lay of the land to find better solutions, faster.

%This paper also presents a  resource (tiny.cc/d-se) for exploring Data-Driven Search-based Software Engineering.  The resource contains 89 artifacts which are related to Data-driven Search-based Software Engineering, divided into 13 groups such as requirements engineering, software product lines, software processes, etc. All the materials in this repository have been   used in recent SE papers; i.e., for all this material, there exist baseline results against which researchers can use to comparatively assess their new ideas.

%This paper tries to answer the following three questions:: (1) What are the various topics addressed by DSE?, (2) What types of data are used by the researchers, and, (3) What research approaches do researchers use? The paper briefly sets out to act as a practical guide to develop new data-driven techniques and also to serve as a teaching resource.
\end{abstract}

@@

The MSR  community has benefited enormously from widely shared datasets.  Such datasets document the canonical problems in a field.
They serve to cluster together like-minded researchers while allowing them to generate reproducible results. Also, such data can be used by
   newcomers to learn the state of the art methods in this field. Further, they enable the mainstay of good science:
reputable, repeatable,  improvable, and even refutable results.
At the time of this writing,   nine of the 50 most cited papers in the last 5 years at IEEE Transactions of Software Engineering {all draw their case studies
from a small number of readily available defect prediction datasets.} 
% \TODO{I'm not sure if it is good to say ``a small number of similar datasets''. What about saying that they all draw their case studies from open datasets?}.

@@

% \begin{figure*}
% { \small
% \begin{tabular}{lp{.26\linewidth}p{.48\linewidth}}
%  \rowcolor{gray} & \textcolor{white}{{\bf MSR}} & \textcolor{white}{{\bf SBSE}}\\ 
%  \textbf{Primary inference} & induction, sumamrization, visualiztion & optimization \\
%  \rowcolor{gray!10}\textbf{Inference speed} & very fast, scalable & becoming faster, more scalable\\
% \textbf{Data} often collected... &
% ... once,  then processed.
% &
% ... on demand
% from  some generator-- which means an SBSE analysis can 
% generate new samples of the data in very  specific regions.
% \\ 
% \rowcolor{gray!10}
% \textbf{Conclusions} often 
% generated via...
% &
% ...a single  execution of a data miner
% (perhaps with some data pre-processing). 
% &
% ...an evolutionary process  where execution $i+1$ is guided
% by the results of execution $i$.
% \\

% \textbf{Canonical   tools} are usually ..
% &
% ... data mining algorithms like  the decision
% tree learners of WEKA~\cite{hall2009weka} or the mathematical modeling tools of R~\cite{rmanual18}.
% &
% ... multi-objective optimization algorithms which may be either home-grown scripts or parts of large toolkits like jMETAL/DEAP used by JAVA/PYTHON programmers (respectively)~\cite{refs2jmetalDEE, DEAP_JMLR2012}.
% \\ 
%  \rowcolor{gray!10}
% \textbf{Canonical   problems} include...
% &
% ...defect prediction~\cite{lessmann2008benchmarking}   or Stackoverflow text mining~\cite{fu2017easy}. 
% &
%  ...configuring a software system~\cite{nair2017faster} or extracting a valid(ish) product from a product line description~\cite{sayyad13b} or minimizing a test suite~\cite{fraser2007redundancy} or selecting screen designs that
% reduce the power consumption  mobile devices
% \\

% \textbf{Results}   assessed by....
% &
% ...a small number of standard measures
% including   recall, precision, or false alarm rates (for discrete classes)
% or magnitude of relative error or standardized error~\cite{Shepperd2012}.
% &
% ... a wide-variety of domain-specific objective.
% What ever the specific objectives, a small number meta-measures are used in many research papers such as the hypervolume or spread (which are ways to characterize how well an SBSE tool explores a space of objectives). \\
% \hline
% \end{tabular}}
% \caption{Some differences between MSR and SBSE. To  misquote George Box, we hope this list is  more useful than  wrong.}\label{fig:diff}
% \end{figure*}

{The similar goals of these two areas, as well as the intrinsic relationship between data mining and optimization algorithms, has been recently inspiring an} increase in methods that combine MSR and SBSE.
A recent {NII Shonan Meeting}  on {\em Data-driven Search-based Software
Engineering} (goo.gl/f8D3EC)   was well attended by over two dozen senior members of the MSR community.
The workshop concluded that (1) mining software repositories could be improved using {tools from the SBSE community}; and that (2) search-based methods can be improved using tools from the MSR community. 
For example:
\begin{itemize}[leftmargin=*]
\item
MSR data mining algorithms can be used to summarize the data, after which SBSE can leap to better solutions, faster~\cite{krall2015gale}.
\item
SBSE {algorithms} can be used to intelligently select 
settings for MSR data mining algorithms (e.g.
such as how many trees should be included in a random
forest~\cite{fu2016tuning}).
\end{itemize}
The workshop also concluded that this community needs more shared  resources 
to help more researchers and educators explore MSR+SBSE.
Accordingly, this paper describes  tiny.cc/data-se,
a collection of artifacts for exploring
data-driven search-based SE (see Figure~1). 
All the materials in this repository
have been used in recent SE papers; i.e., for all this material, there exist baseline results against which researchers can use to comparatively assess their new ideas.
%\TODO{Re: fig. 1, are we allowed to use Abhaham's nice piece of art?}

It has taken several years to build this resource. Prior to its
existence, we explored data-driven search-based SE
prototypes on tiny toy tasks that proved 
uninteresting to 
 reviewers from SE venues. 
Recently we have much more success in terms of novel
research results
(and publications at SE forums) after 
expanding that collection
to include models
of, e.g., software product lines, requirements, and
agile software projects. 
As such we have found it to be a very useful resource
which we now offer to the MSR community.

% XXX optimisation

% It turns out that SBSE has much to offer MSR, hyper-parameter optimization of data miners or data pre-processers. novel solutions to hard configuration problems. direct application of user criteria to problems. further, MSR has much to offer SBSE particularly in the area of landscape analysis and explanation. SBSE tools walk over a landscape of potential solutions. When MSR tools are used to

% XXX we show that,  syntactically, there is much overlap between design choices in SBSE and MSR. Hence we can say that learning and optimization go hand in hand and we should not treat both of these techniques in isolation. Instead, we should exchange ideas between these two domains. We call the marriage of these two fields by Data-Driven Search-based Software Engineering (DSE\footnote{DDSSE might be a more appropriate abbreviation but let us remove redundancy in the name.}). We appeal to the community that it is time to modify our approaches. It is not longer SBSE or MSR. Let us tie these two domain and exchange ideas to bring the learning and searching closer---thereby learning from each other. \footnote{The geneses of the ideas presented in this paper happened in the \href{http://shonan.nii.ac.jp/shonan/blog/2016/09/08/data-driven-search-based-software-engineering/}{No.105 Data-Driven Search-Based Software Engineering}, where leading practitioners came together to propose and exchange ideas.}

@@

\begin{figure}[t]

{\center
\fbox{ \includegraphics[width=3in]{img/page1.png}}}
\caption{http://tiny.cc/data-se}\label{fig:one}
\end{figure}

@@

                \textbf{Representation: } {This defines how solutions $x$ are represented internally by the algorithm.
                Examples of representations are Boolean or numerical vectors, but more complex representations are also possible. The space of all values that can be represented is the} \textit{Decision Space}.
                % The representation of these solutions is significant to generate the landscape of the problem.

@@

                \textbf{Operators: } {These are operators that (1) generate new solutions based on one (e.g., mutation operator) or more (e.g., crossover or recombination operators) existing solutions, and (2) operators that select solutions to pass to the aforementioned operators or to survive for the next iteration of the algorithm. The operators (2) typically apply some pressure towards selecting better solutions either deterministically (e.g., elitism operator) or stochastically.} 
                % \TODO{If space allows, we can mention survival of the fittest.} % They can be used along with an}\TODO{I haven't finished this change yet. I have to come back later.} 
                \textit{Elitism operator} simulates the `survival of the fittest' strategy, i.e., eliminates not so good solutions thereby preserving the good solutions in the population.

@@

                            \textbf{Approximation: } Additive/multiplicative Approximation is an alternative measure which can be computed in linear time (w.r.t. to the number of objectives). It is the multi-objective extension of the concept of approximation encountered in theoretical computer science. 
                            % The intuition is that the search process aims at finding a set of solutions with a small approximation ratio, so why not simply compute the approximation ratio (as?

@@

\item
Mission-critical systems are risk averse and may accept very high false alarm rates,
just as long as they catch any life-threatening possibility. That is, such projects
do not care about effort- they want to {\em maximize recall} regardless of any impact
that might have on the false alarm rate.
\item  Suppose a new hire wants
 to impress their manager. That
 new hire might want to ensure that no result presented to  management contains  true negative;
i.e. they wish to {\em maximize precision}.
\item
Some communities do not care about   low precision,
just as long as a small fraction the data is returned. Hayes, Dekhytar, \& Sundaram call this fraction
{\em selectivity} and offer an
extensive discussion of the merits of this measure~\cite{hayes06}.
\end{enumerate}
\\ \hline
\rowcolor{gray!10}
Beyond defect prediction are other goals that combine defect prediction with other economic
factors:
\begin{enumerate}[leftmargin=0.4cm]
\setcounter{enumi}{3}
\item
Arisholm~\&~Briand~\cite{arisholm06},  Ostrand \& Weyeuker~\cite{ostrand04} and Rahman et al.~\cite{rahman12}
say that a defect predictor should maximizing {\em reward}; i.e. find the fewest lines of code
that contain the most bugs.
\item In other work, Lumpe et al. are concerned about
 {\em amateur  bug fixes}
%  ; i.e. those that made by programmers to regions of the code that are unfamiliar, to them
~\cite{me11f}.
Such amateur fixes are highly correlated to errors and, hence, to
avoid such incorrect bug fixes, we have to optimize
for finding the most number of bugs in regions that {\em the most programmers have worked with before}.
\item In {\em better-faster-cheaper} setting, one seeks  project changes that lead
to fewer defects and faster development times using fewer resources~\cite{elrawas10,me07f,me09a,me09f}.
\item
Sayyad~\cite{sayyad13a,sayyad13b} explored models of software product
lines whose value propositions are defined by five objectives.
\end{enumerate}
\\ \hline
\rowcolor{gray!10}
All the above measures relate to the tendency of a predictor to find something. Another measure could be {\em variability} of predictor.
\begin{enumerate}[leftmargin=0.4cm]
\setcounter{enumi}{7}
\item
In their study on reproducibility of SE results,
 Anda, Sjoberg and Mockus advocate using the coefficient of variation ($CV=\frac{stddev}{mean}$).
Using this measure, they defined {\em reproducibility} as $\frac{1}{CV}$~\cite{mockus09}.
\end{enumerate}\\\hline
\end{tabular}
\caption[Different users value different things.]{Different users value different things.
% Technical note:  some of
% these goals are defined in terms of
% Figure~\ref{fig:criteria}.
}\label{fig:goals}
\end{figure}

%  In  a very loose sense, we can associate \textit{learning} with MSR, since most of the work in this area attempts to learn from massive amounts of data, and \textit{optimization} with SBSE. Note we stress that this is only a loose association since learning and optimization can are mutually inclusive (see examples, below).

%  The rest of this section compares these two fields.

% \noindent\textbf{Data:} SBSE predominantly uses meta-heuristics algorithms such as NSGA-II~\cite{deb2000fast}, SPEA~\cite{zitzler2001spea2} to navigate the space of possible options. These algorithms rely on fitness functions to differentiate between good and bad solutions. This means there is no universal fitness function, for every problem, there is an associated fitness function. Similarly in MSR, which uses different kinds of data miners to model the given data (or a problem). Different kinds of data miners work best of different kinds of data. This goes to show both techniques of MSR and SBSE needs to be adjusted to fit the needs of the problem or the practitioner.

% \noindent\textit{Design Choice:} The choice of the fitness function (in SBSE) and data miner (in MSR) depends on the type of data used for that experiments.

% \noindent\textbf{Goals:} In SBSE, the meta-heuristic algorithms used in an experiment depends on the number of goals of the experiment. A single goal or single-objective problem can be solved using algorithms such as \textit{Simulated Annealing}~\cite{van1987simulated} or hill climbing~\cite{rudlof1997stochastic}, whereas for multiple goal or multi-objective problems can be solved using algorithms such as NSGA-II, SPEA, MOEA/D~\cite{zhang2007moea}. In MSR, if the data table has no goal columns, then this is an \textit{unsupervised learning problem} which can be addressed by (say) finding clusters of similar rows using, say, K-means or expectation maximization. An alternate approach, taken by the Apriori association rule learner, is to assume that every column is a goal and to look for what combinations of any values predict for any combination of any other. If a table has one goal, then this is a \textit{supervised learning problem} where the task is to find combinations of values from the other columns that predict for the goal values. Note that for datasets with one discrete goal feature, it is common to call that goal the class of the dataset. If a table has multiple goals, then the ML model (or combination of models) should trade-off in goal space by domination predicates (dominance counts, dominance depth, dominance ranks).

% \noindent\textit{Design Choice:} The meta-heuristic algorithm (SBSE) or the data miner (MSR) used for the experiments must be adjusted based on the number of goals in the experiment.

% \noindent\textbf{Computational Overhead:} In SBSE, the size of the search space and the number of constraints in it, govern the computational budget of the experiment. Larger the search space or a highly constrained space means the meta-heuristic algorithms requires long run times or high computational budget. In MSR, the size of the dataset dictates the time required to train the chosen ML algorithm, and hence various engineering decisions need to be taken to handle the size of the data.

% \noindent\textit{Design Choice:} The computational budget required to run both SBSE and MSR techniques are governed by the size of the search space and data respectively.

% \noindent\textbf{Parameter Tuning:} In SBSE, the convergence of the meta-heuristic algorithms are governed by the parameters of the meta-heuristic algorithm~\cite{eiben2011parameter}. Similarly, in MSR, the effectiveness of the ML algorithm used is controlled by its various parameters~\cite{fu2016tuning, fu2016differential, tantithamthavorn2016automated}.

% \noindent\textit{Design Choice:} The performance of the meta-heuristic algorithm (in SBSE), and machine learning algorithms (in MSR) is governed by the parameters used in them.

@@

 Figure~\ref{fig:sbse_crash} provides a (very) short tutorial on SBSE and  Figure~\ref{fig:diff} characterizes some of the differences between MSR 
%  \TODO{Are we using the term SA or MSR? Maybe we should stick to MSR? Please check the whole paper for consistency.} 
and SBSE.

@@

% If MSR was completely different to SBSE (as suggested by Figure~\ref{fig:sbse_crash}), 
% then there would be no point
% to this paper. This section argues combining both methods is insightful and useful.

% A recent study by Chen et al.~\cite{xxChenSampleXXX}  illustrates the benefits
% of combining MSR+SBSE. In that study, Chen was applying SBSE 
% to many of the models in tiny.cc/d-se to 
% to optimize   decisions about software processes options, generating product lines,
% and configuring the LINUX kernel. Reviewers of that work requested that his SBSE
% results be compared to some baseline exhaustive search. According, Chen
% generated, then pruned, 10,000 random candidate solutions  using a pairwise comparison procedure.
% These results were compared with state-of-the-art
% SBSE methods that using genetic operators (combine, mutate, select, repeat)
% to carefully explore the same models.

% As expected, the exhaustive search ran impractically slowly (54 hours)
% while the SBSE methods ran two orders of magnitude taster (24 minutes).
% On the other hand,  a statistical comparison showed that the exhaustive approach
% found as good, or better, solutions that the state-of-the-art SBSE
% methods $\frac{44}{48}=92$\% in comparisons.

% This experiment suggests the following exciting possibility.

Consider the following. The MSR
community knows how to deal with large sets of data. The SBSE community knows how to take
clues from different regions of data, then combine them to generate better solutions.
If the two ideas were combined, then  MSR could be  {\em sampling} technology to quickly
find the regions where SBSE  can learn {\em  optimizations}. If so:
\begin{quote}
\centering
{\bf {\em   MSR  methods can ``supercharge''    SBSE.}}
\end{quote}
For a very specific example of this ``supercharging'', consider active learning
with Gaussian Process Models (GPM) used for multi-objective optimization
by the machine learning community~\cite{zuluaga2016varepsilon}.  Active learners assume that evaluating one candidate
is very expensive. For example, in software engineering, ``evaluating'' a test suite
might mean re-compiling
the entire system then re-running all tests. When evaluation is so slow,
an active learner reflects on the examples seen so far to find the next most informative
example to evaluate next. One way to do this is to use GPMs  to
find which parts of a model have maximum variance in their predictions 
(since sampling
in such high-variance regions serves to most constrain the model).

@@

Not only is   MSR useful for   SBSE, but so too:
\begin{quote}
\centering
{\bf {\em SBSE methods can    ``supercharge''    MSR.}}
\end{quote}
The standard example here is parameter tuning. Most data mining algorithms come with tuning
parameters that have to be set via expert judgment. Much recent work shows that for
MSR problems such as defect prediction and text mining, SBSE can automatically find settings that are far superior to the default settings. For example:
\begin{itemize}[leftmargin=*]
 \item
   When performing defect prediction, various groups report that SBSE methods can find new settings that dramatically improve the performance of the learned model~\cite{fu2016tuning,tantithamthavorn2016automated, Tantithamthavorn2018}.

@@

\end{itemize} 
Note that all the above used case study material from tiny.cc/data-se.

% \definecolor{co1}{RGB}{249,239,230}
% \definecolor{co2}{RGB}{255,192,202}
% \definecolor{co3}{RGB}{144,237,144}
% \newcommand{\yy}[1]{\cellcolor{co3} {\textit{#1}}}
% \newcommand{\nn}[1]{\cellcolor{co2} {\textit{#1}}}
% \newcommand{\sAM}[1]{\cellcolor{co1} {\textit{#1}}}
% \begin{figure}[!b]
% {\footnotesize
% \begin{tabular}{rr|c|c|c|c}
% &&\multicolumn{4}{c}{Four multi-objective evaluation criteria}\\\cline{3-6}
% &          & Generational & Generated & Pareto  & Hyper-   \\
% n&model     & Distance     & Spread    & Front Size   & volume    \\\hline
% 1&osp       &    \yy{0.5}          &        \yy{1.95}   &    \yy{0.46}    &     \yy{0.6}       \\
% 2&ops2      &    \yy{1.30}         &     \yy{0.82}      &   \yy{0.72}     &    \yy{0.65}        \\
% 3&ground    &     \nn{0.79}        &      \yy{0.86}     &    \yy{0.71}    &   \sAM{0.30}         \\
% 4&flight    &    \yy{1.96}         &   \yy{0.86}        &     \yy{0.42}     &   \yy{0.52}         \\
% 5&pom3a     &     \yy{0.79}         &   \nn{0.53}         &      \yy{01.30}  &    \yy{0.85}        \\
% 6&pom3b     &        \yy{0.75}     &    \yy{0.43}        &   \yy{0.56}      &  \yy{0.85}           \\
% 7&pom3c     &     \yy{0.69}         &   \yy{0.42}         &     \yy{0.82}    &  \nn{1.03}          \\
% 8&webportal &    \yy{0.63}          & \yy{0.90}          &    \yy{1.86}    &    \sAM{0.63}         \\
% 9&eshop     &    \yy{0.74}         &     \sAM{0.29}      &    \yy{1.23}    &     \yy{1.29}        \\
% 10&fiasco    &      \yy{1.97}       &        \sAM{0.49}    &    \yy{1.99}    &        \sAM{0.23}    \\
% 11&freebsd   &     \yy{0.79}        &      \sAM{0.22}      &    \yy{1.98}    &     \yy{0.63}        \\
% 12&linux     &     \yy{0.72}        &     \sAM{0.13}      &  \yy{1.99}      &        \yy{1.97}    \\\hline
% &same + better& 11/12           & 11/12         & 12/12     & 11/12
% \end{tabular}}
% \caption{{\sc GroundTruth} vs state-of-the-art: How often is ground truth worse, same, or better?
% Summarized from 
% \fig{boxplot}. Color patterns are the same as \fig{boxplot}. Decimal in each cell is the effect size.  Generating and evaluating all the models in this figure took 52 hours of CPU.}\label{fig:sum1}
% \end{figure}

 Yet another, subtler, benefit of combining MSR+SBSE relates to the exploration of competing
 objectives.
 We note that  
 software engineering tasks rarely involve a
single goal. For example, when a software engineer
is testing a software, she may be interested in
finding the highest possible number of software
defects at the same time as minimizing the time
required for testing. Similarly, when a software
engineer is planning the development of a software,
he/she may be interested in minimizing the number of
defects, the effort required to develop the software
and the cost of the software. The existence of {\em
multiple goals} necessarily implies that such problems should be solved via
a   multi-objective optimizers.

There are many such goals. For example, 
let $\{A,B,C,D\}$ denote the
true negatives,
false negatives,
false positives, and
true positives
(respectively) found by a software defect detector.
Also, let $L_A L_b, L_c, L_d$ be the lines of code
seen in the parts of system that fall
into $A,B,C,D$. Given these definitions then

@@

The important point here is that, in terms of evaluation criteria,  the above are just the tip of the iceberg.
Figure~\ref{fig:goals} lists several other criteria that have appeared recently in the literature. Note that this list is hardly complete-- SE has many sub-problems and many of those
problems deserve their own specialized evaluation criteria.

>>>>

\documentclass[sigconf]{acmart}

@@

\begin{document}

\copyrightyear{2018} 
\acmYear{2018} 
\setcopyright{acmcopyright}
\acmConference[MSR '18]{MSR '18: 15th International Conference on Mining Software Repositories }{May 28--29, 2018}{Gothenburg, Sweden}
\acmBooktitle{MSR '18: MSR '18: 15th International Conference on Mining Software Repositories , May 28--29, 2018, Gothenburg, Sweden}
\acmPrice{15.00}
\acmDOI{10.1145/3196398.3196442}
\acmISBN{978-1-4503-5716-6/18/05}

\title{Data-Driven Search-based Software Engineering}
% \titlenote{Produces the permission block, and
%   copyright information}
% \subtitle{Extended Abstract}
% \subtitlenote{The full version of the author's guide is available as
%   \texttt{acmart.pdf} document}

\author{Vivek Nair, Amritanshu Agrawal, Jianfeng Chen, Wei Fu, George Mathew, Tim Menzies, Leandro Minku*, Markus Wagner$^+$, Zhe Yu}
\affiliation{%
  \institution{North Carolina State University, USA; *University of Leicester,UK; $^+$The University of Adelaide, Australia}
}
\email{}

\begin{abstract}
This paper introduces Data-Driven Search-based Software Engineering (DSE), which combines insights from Mining Software Repositories (MSR) and Search-based Software Engineering (SBSE). While MSR formulates software engineering problems as data mining problems, SBSE reformulate SE problems as optimization problems and use meta-heuristic algorithms to solve them. Both MSR and SBSE share the common goal of providing insights to improve software engineering. The algorithms used in these two areas also have intrinsic relationships.  
We, therefore, argue that combining these two fields
is useful for situations (a)~which require learning from a large data
source or (b)~when optimizers need to know the lay of the land to find better solutions, faster.

@@

This paper also presents a  resource (tiny.cc/data-se) for exploring DSE.  The resource contains 89 artifacts which are related to DSE,
divided into 13 groups such as requirements engineering, software product lines, software processes.
All the materials in this repository
have been used in recent software engineering papers; i.e., for all this material, there exist baseline results against which researchers can comparatively assess their new ideas.
\end{abstract}

@@

The MSR  community has benefited enormously from widely shared datasets.  Such datasets document the canonical problems in a field.
They serve to cluster together like-minded researchers while allowing them to generate reproducible results. Also, such data can be used by newcomers to learn the state of the art methods in this field. Further, they enable the mainstay of good science:
reputable, repeatable,  improvable, and even refutable results.
At the time of this writing,   nine of the 50 most cited papers in the last 5 years at IEEE Transactions of Software Engineering {all draw their case studies
from a small number of readily available defect prediction datasets.}

@@

{The similar goals of these two areas, as well as the intrinsic relationship between data mining and optimization algorithms, has been recently inspiring an} increase in methods that combine MSR and SBSE.
A recent {NII Shonan Meeting}  on {\em Data-driven Search-based Software
Engineering} (goo.gl/f8D3EC)   was well attended by over two dozen senior members of the MSR community.
The workshop concluded that (1) mining software repositories could be improved using {tools from the SBSE community}; and that (2) search-based methods can be enhanced using tools from the MSR community. 
For example:
\begin{itemize}[leftmargin=*]
\item
MSR data mining algorithms can be used to summarize the data, after which SBSE can leap to better solutions, faster~\cite{krall2015gale}.
\item
SBSE {algorithms} can be used to select intelligently 
settings for MSR data mining algorithms (e.g.
such as how many trees should be included in a random
forest~\cite{fu2016tuning}).
\end{itemize}
The workshop also concluded that this community needs more shared resources to help more researchers and educators explore MSR+SBSE.
Accordingly, this paper describes  tiny.cc/data-se,
a collection of artifacts for exploring
data-driven search-based SE (see Figure~1). 
All the materials in this repository
have been used in recent SE papers; i.e., for all this material, there exist baseline results against which researchers can use to assess their new ideas comparatively.

It has taken several years to build this resource. Before its
existence, we explored data-driven search-based SE
prototypes on small toy tasks that proved uninteresting to reviewers from SE venues. 
Recently we have much more success in terms of novel
research results
(and publications at SE forums) after 
expanding that collection
to include models
of, e.g., software product lines, requirements, and
agile software projects. 
As such we have found it to be a handy resource
which we now offer to the MSR community.

@@

\begin{figure}[t]
 \setlength{\fboxsep}{0.5pt}

\fbox{ \includegraphics[width=3.2in]{img/page1.png}}
\caption{http://tiny.cc/data-se}\label{fig:one}
\end{figure}

@@

                \textbf{Representation: } {This defines how solutions $x$ are represented internally by the algorithm.
                Examples of representations are Boolean or numerical vectors, but more complicated representations are also possible. The space of all values that can be represented is the} \textit{Decision Space}.

@@

                \textbf{Operators: } {These are operators that (1) generate new solutions based on one (e.g., mutation operator) or more (e.g., crossover or recombination operators) existing solutions, and (2) operators that select solutions to pass to the aforementioned operators or to survive for the next iteration of the algorithm. The operators (2) typically apply some pressure towards selecting better solutions either deterministically (e.g., elitism operator) or stochastically.} 
                \textit{Elitism operator} simulates the `survival of the fittest' strategy, i.e., eliminates not so good solutions thereby preserving the good solutions in the population.

@@

                            \textbf{Approximation: } Additive/multiplicative Approximation is an alternative measure which can be computed in linear time (w.r.t. to the number of objectives). It is the multi-objective extension of the concept of approximation encountered in theoretical computer science.

@@

\item
Mission-critical systems are risk-averse and may accept very high false alarm rates, just as long as they catch any life-threatening possibility. That is, such projects
do not care about effort- they want to {\em maximize recall} regardless of any impact
that might have on the false alarm rate.
\item  Suppose a new hire wants to impress their manager. That the new hire might want to ensure that no result presented to  management contains  true negative;
i.e., they wish to {\em maximize precision}.
\item
Some communities do not care about low precision, just as long as a small fraction the data is returned. Hayes, Dekhytar, \& Sundaram call this fraction
{\em selectivity} and offer an extensive discussion of the merits of this measure~\cite{hayes06}.
\end{enumerate}
\\ \hline
\rowcolor{gray!10}
Beyond defect prediction are other goals that combine defect prediction with other economic
factors:
\begin{enumerate}[leftmargin=0.4cm]
\setcounter{enumi}{3}
\item
Arisholm~\&~Briand~\cite{arisholm06},  Ostrand \& Weyeuker~\cite{ostrand04} and Rahman et al.~\cite{rahman12}
say that a defect predictor should maximize {\em reward}; i.e., find the fewest lines of code
that contain the most bugs.
\item In other work, Lumpe et al. are concerned about
 {\em amateur  bug fixes}

~\cite{me11f}.
Such amateur fixes are highly correlated to errors and, hence, to
avoid such incorrect bug fixes; we have to optimize
for finding the most number of bugs in regions that {\em the most programmers have worked with before}.
\item In {\em better-faster-cheaper} setting, one seeks  project changes that lead
to fewer defects and faster development times using fewer resources~\cite{elrawas10,me07f,me09a,me09f}.
\item
Sayyad~\cite{sayyad13a,sayyad13b} explored models of software product
lines whose value propositions are defined by five objectives.
\end{enumerate}
\\ \hline
\rowcolor{gray!10}
All the above measures relate to the tendency of a predictor to find something. Another measure could be {\em variability} of the predictor.
\begin{enumerate}[leftmargin=0.4cm]
\setcounter{enumi}{7}
\item
In their study on reproducibility of SE results,
 Anda, Sjoberg and Mockus advocate using the coefficient of variation ($CV=\frac{stddev}{mean}$).
Using this measure, they defined {\em reproducibility} as $\frac{1}{CV}$~\cite{mockus09}.
\end{enumerate}\\\hline
\end{tabular}
\caption[Different users value different things.]{Different users value different things.
}\label{fig:goals}
\end{figure}

@@

 Figure~\ref{fig:sbse_crash} provides a (very) short tutorial on SBSE and  Figure~\ref{fig:diff} characterizes some of the differences between MSR 
and SBSE.

@@

Consider the following. The MSR
community knows how to deal with large sets of data. The SBSE community knows how to take
clues from different regions of data, then combine them to generate better solutions.
If the two ideas were combined, then  MSR could be  {\em sampling} technology to quickly
find the regions where SBSE  can learn {\em  optimizations}. If so:
\begin{quote}
\centering
{\bf {\em   MSR  methods can ``supercharge''    SBSE.}}
\end{quote}
For a concrete example of this ``supercharging'', consider active learning
with Gaussian Process Models (GPM) used for multi-objective optimization
by the machine learning community~\cite{zuluaga2016varepsilon}.  Active learners assume that evaluating one candidate
is very expensive. For example, in software engineering, ``evaluating'' a test suite
might mean re-compiling the entire system then re-running all tests. When the evaluation is so slow,
an active learner reflects on the examples seen so far to find the next most informative
example to evaluate next. One way to do this is to use GPMs to
find which parts of a model have maximum variance in their predictions 
(since sampling
in such high-variance regions serves to most constrain the model).

@@

Not only is   MSR useful for   SBSE, but so too:
\begin{quote}
\centering
{\bf {\em SBSE methods can    ``supercharge''    MSR.}}
\end{quote}
The standard example here is parameter tuning. Most data mining algorithms come with tunable parameters that have to be set via expert judgment. Much recent work shows that for
MSR problems such as defect prediction and text mining, SBSE can automatically find settings that are far superior to the default settings. For example:
\begin{itemize}[leftmargin=*]
 \item
   When performing defect prediction, various groups report that SBSE methods can find new settings that dramatically improve the performance of the learned model~\cite{fu2016tuning,tantithamthavorn2016automated, Tantithamthavorn2018}.

@@

\end{itemize} 
Note that all the above-used case study material is from tiny.cc/data-se.

 Another, subtler, benefit of combining MSR+SBSE relates to the exploration of competing
 objectives.
 We note that software engineering tasks rarely involve a single goal. For example, when a software engineer
is testing a software, she may be interested in finding the highest possible number of software defects at the same time as minimizing the time required for testing. Similarly, when a software
engineer is planning the development of a software,
he/she may be interested in reducing the number of
defects, the effort required to develop the software and the cost of the software. The existence of {\em
multiple goals} necessarily implies that such problems should be solved via a multi-objective optimizer.

There are many such goals. For example, 
let $\{A,B,C,D\}$ denote the
true negatives,
false negatives,
false positives, and
true positives
(respectively) found by a software defect detector.
Also, let $L_A L_b, L_c, L_d$ be the lines of code
seen in the parts of the system that fall
into $A, B, C, D$. Given these definitions then

@@

The critical point here is that, in terms of evaluation criteria,  the above are just the tip of the iceberg.
Figure~\ref{fig:goals} lists several other criteria that have appeared recently in the literature. Note that this list is hardly complete-- SE has many sub-problems and many of those
problems deserve their specialized evaluation criteria.

SBSE is one way to build inference systems that are specialized to specialized evaluation
criteria. SBSE systems accept as input some function that assesses candidates on multiple
criteria (and that function is used to guide the inference of the SBSE tool).
Several recent results illustrate the value of using a wider range of evaluation criteria
to assess our models:
\begin{itemize}[leftmargin=*]
\item
Sarro et al.~\cite{sarro2016multi}  used SBSE tools that assessed software effort estimation tools
not only by their predictive accuracy but also by the confidence of those predictions.
These multi-objective methods out-performed the prior state of the art in effort estimation. 
{Prior work also used multi-objective methods to boost the predictive performance of ensembles for
software effort estimation~\cite{minku2013}.}
\item
Agrawal et al.~\cite{agrawalwrong} used SBSE tools to tune text mining tools for StackOverflow.
Standard text mining tools can suffer from ``order effects'' in which changing the order
of the training data leads to large-scale changes in the learned clusters.
To fix this, Agrawal et al. tuned the background priors
of their Latent Dirichlet allocation (LDA) algorithm to maximize the stability
of the learned clusters.  Classifiers based on these stabilized clusters performed better than those based on the clusters learned by standard LDA.
\end{itemize}
